Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-08-05 exp1/iswc2013.tex
Comment on DoE SotA
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@638 43ef1190-90fd-4dd7-a769-d0121f02b80e
Slight reformulations
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@639 43ef1190-90fd-4dd7-a769-d0121f02b80e

Finally, we have only employed the simplest parts of the DoE theory.
What has been presented here is part of a much more general formalism
known as Orthogonal Arrays. The use of orthogonal arrays allow for
different numbers of levels, for much greater flexibility in total run
size, and for non-regular designs that can provide a good fit for the
complex problem of SPARQL endpoint evaluations.

>>>>

In this paper, we have only employed the simplest parts of the DoE theory.
What has been presented here is part of a much more general formalism
known as Orthogonal Arrays. The use of orthogonal arrays allow for
different numbers of levels, for much greater flexibility in total run
size, and for non-regular designs that can provide a good fit for the
complex problem of SPARQL endpoint evaluations.

Finally, as each run is cheap, and the experiment can usually run
without human intervention, we believe it is interesting as a case for
advancing the state of the art of DoE.
